Understanding Supersymmetry

### 2021-09-09 alpha/SUSY/susy.tex
Add comments on R symmetry in SUSY & style tweaks

\begin{document}
\maketitle
\pagenumbering{arabic}
\thispagestyle{empty}

@@

\addtocounter{section}{-1}
\section{Main References}
\raggedright
\begin{itemize}
\item Primary:
	\begin{itemize}[itemsep=\parskip]%[leftmargin=2em]
	\item[\cite{Argyres:1996abc}]\fullcite{Argyres:1996abc}
		\par \textit{Recommended by Yanyan.}

@@

\section{Algebra \& Unitary Representations}
	\speaker{Yanyan ``Handsome'' Li}\\
	\references{
	\begin{enumerate}[noitemsep,topsep=0pt]
	\item \textcite{Argyres:1996abc}, \S5
	\item \textcite{Wess:1992cp}, Chapter II
	\end{enumerate}
	}\vspace{.5\baselineskip}

@@

	There is more story behind \eqref{eq:fermion_number_R_symmetry}; in fact, $F$ generates an automorphism of the SUSY algebra. It is part of the \textit{R-symmetry}, and can be added to the algebra as an extension. 
	In Lorentzian 4D, the maximal amount of R-symmetry\footnote{
		This comes from the maximal extension of the SUSY algebra. It is common that, given a specific theory, only some of the R-symmetries are preserved, while others are broken. 
	} is $\mrm{U}(\mcal{N})$, and $F$ is the generator of the $\mrm{U}(1)_V$ subgroup; here the \mbox{subscript V} stands for ``vector'', meaning that the supercharge $Q^i$ transforms as a vector with index $i$ under the $\mrm{U}(1)_V$ action: all components labeled by $i$ gains the same phase shift under $\mrm{U}(1)$.

@@

	\newparagraph
	A more refined invariant in 2D that involves only the left-moving (or right-moving) part of theory is the \textit{elliptic genus}. For 2D $\mcal{N} = (2,2)$ superconformal theory (SCFT), the fermion number:
	\begin{equation}
		F = F_V = J_0 + \bar{J}_0
	\end{equation}
	Here $J(z),\bar{J}(\bar{z})$ are bosonic currents. They can be understood as the infinite dimensional enhancement of the R-symmetry generators in an SCFT, while their 0-modes $J_0,\bar{J}_0$ corresponds to the original R-symmetry generators in the SUSY algebra. $F_V = J_0 + \bar{J}_0$ is the $\mrm{U}(1)_V$ generator, while $F_A = \bar{J}_0 - J_0$ is the $\mrm{U}(1)_A$ generator. The \mbox{subscript A} stands for ``axial'', meaning that $Q^i$ transforms in an axial representation of $\mrm{U}(1)$, where the group action discriminates between left and right-handed components. For more on this, see e.g.~\cite{MauricioStuff}.

>>>>

\begin{document}
\maketitle
\pagenumbering{arabic}

@@

%\pagebreak\thispagestyle{headless}
\addtocounter{section}{-1}
\section{Main References}
\raggedright
\begin{itemize}
\item Primary:
	\begin{itemize}[itemsep=\parskip]%[leftmargin=2em]
	\item[\cite{Argyres:1996abc}]\fullcite{Argyres:1996abc}
		\par \textit{Recommended by Yanyan.}

@@

\pagebreak\thispagestyle{headless}
\section{Algebra \& Unitary Representations}
	\speaker{Yanyan ``Handsome'' Li}\\
	\references{
	\begin{enumerate}[noitemsep,topsep=0pt]
	\item \textcite{Argyres:1996abc}, \S5
	\item \textcite{Wess:1992cp}, Chapter II
	\end{enumerate}
	}\vspace{.5\baselineskip}

@@

	There is more story behind \eqref{eq:fermion_number_R_symmetry}; in fact, $F$ generates an automorphism of the SUSY algebra. It is part of the \textit{R-symmetry}, and can be added to the algebra as an extension. 
	In Lorentzian 4D, the maximal amount of R-symmetry is $\mrm{U}(\mcal{N})$, and $F$ is the generator of the central $\mrm{U}(1)$ subgroup:
	\begin{equation}
		\mrm{U}(\mcal{N})
		= \mrm{U}(1) \rtimes \mrm{SU}(\mcal{N})
	\end{equation}
	$\mrm{U}(\mcal{N})$ comes from the maximal extension of the SUSY algebra. It is common that, given a specific theory, only some of the R-symmetries are preserved, while others are broken. Even the fermion number $e^{i\theta F} \in \mrm{U}(1)$ can be broken, but it seems that the $\mbb{Z}_2$ subgroup generated by $e^{i\pi F} = (-1)^F$ always survives \needcites.

@@

	\newparagraph
	A more refined invariant in 2D that involves only the left-moving (or right-moving) part of theory is the \textit{elliptic genus}. For 2D $\mcal{N} = (2,2)$ superconformal theory (SCFT), the fermion number:
	\begin{equation}
		F = F_V = J_0 + \bar{J}_0
	\end{equation}
	Here $J(z),\bar{J}(\bar{z})$ are bosonic currents. They can be understood as the infinite dimensional enhancement of the R-symmetry generators in an SCFT, while their 0-modes $J_0,\bar{J}_0$ corresponds to the original R-symmetry generators in the SUSY algebra. $F_V = J_0 + \bar{J}_0$ is the $\mrm{U}(1)_V$ generator, while $F_A = \bar{J}_0 - J_0$ is the $\mrm{U}(1)_A$ generator. 
	The \mbox{subscript V} stands for ``vector'', meaning that the supercharge $Q^i$ transforms as a vector with index $i$ under the $\mrm{U}(1)_V$ action: all components labeled by $i$ gains the same phase shift under $\mrm{U}(1)$. The \mbox{subscript A} stands for ``axial'', meaning that $Q^i$ transforms in an axial representation of $\mrm{U}(1)$, where the group action discriminates between left and right-handed components\footnote{
		This might generate some confusions when compared to 4D: if we think of $Q,\bar{Q}$ as two components of a Majorana spinor (in the Weyl basis), then the fermion number $\mrm{U}(1)$ looks like an \textit{axial} symmetry, as is given in \eqref{eq:fermion_number_R_symmetry}. This is indeed the case in 4D, where charge conjugation switches $Q$ and $\bar{Q}$, as described in \S1.1. We will come back to this in \S\ref{subsect:anomaly}, where we discuss axial anomaly.

		However, charge conjugation in 2D looks very different: it actually switches between $Q_+$ and $Q_-$, where $\mquote{\pm}$ is the $\mcal{N} = 2$ indices. This is consistent with our discussions in \S1.1. 
		For example, a chiral $(2,0)$ theory is constructed not by throwing away $\bar{Q}$, but by throwing away $Q_-$ and $\bar{Q}_-$; see \S12.5.2 of \textit{Mirror Symmetry} \cite{Hori:2003ic}. 
	}.
